---
title: "Tabset Example"
author: "quartify"
description: "Demonstration of tabset functionality in quartify"
format:
  html:
    embed-resources: true
    code-fold: false
    number-sections: true
toc: true
toc-title: Sommaire
toc-depth: 4
toc-location: left
execute: 
  eval: false
  echo: true
output:
  html_document:
  output-file: example_tabset.html
---




## Introduction

This example demonstrates how to use tabsets in quartify to create
tabbed content panels in your Quarto HTML documents.

## Data Analysis with Tabs

We'll explore the iris dataset using different approaches shown in tabs.

::: {.panel-tabset}

## Summary Statistics

Here are the basic summary statistics for the iris dataset:



```{r}
summary(iris)
```


## Data Structure

Let's examine the structure of the data:



```{r}
str(iris)
```


## First Rows

Here are the first few rows of the dataset:



```{r}
head(iris, 10)
```


:::

## Visualization Examples

Another tabset example with different plots.

::: {.panel-tabset}

## Scatter Plot

Relationship between Sepal Length and Petal Length:



```{r}
plot(iris$Sepal.Length, iris$Petal.Length,
     col = iris$Species,
     xlab = "Sepal Length",
     ylab = "Petal Length",
     main = "Sepal vs Petal Length")
legend("topleft", legend = levels(iris$Species), col = 1:3, pch = 1)
```


## Box Plot

Distribution of Sepal Length by Species:



```{r}
boxplot(Sepal.Length ~ Species, data = iris,
        main = "Sepal Length by Species",
        xlab = "Species",
        ylab = "Sepal Length",
        col = c("red", "green", "blue"))
```


## Histogram

Distribution of Petal Width:



```{r}
hist(iris$Petal.Width,
     main = "Distribution of Petal Width",
     xlab = "Petal Width",
     col = "lightblue",
     breaks = 20)
```


:::

## Conclusion

Tabsets allow you to organize related content in a compact, interactive way.
They're perfect for comparing different analyses or visualization approaches.
